P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2025-04-25 sage_latex_template/manuscript.tex
First review changes
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

@@

>>>>

% Changes during review
\newcommand{\RMchange}[1]{{\setlength{\fboxsep}{0pt}\colorbox{purple!70}{#1}}}
%\newcommand{\RMchange}[1]{#1}

@@

\begin{table*}[htb]
    \centering
    \begin{tabular}{c|c|c|c|c}
%        \hline
        Variant & pairs-fn & mdbench-fn & pairs-hn & mdbench-hn \\
        \hline
        Ice Lake & 0.962 & 1.019 & 1.662 & 1.595 \\
        Milan & 0.908 & 0.883 & 1.354 & 1.367 \\
        A40  & 26.452 & 27.025 & 29.688 & --- \\
        A100 & 75.113 & 87.381 & 87.968 & --- \\
%        \hline
    \end{tabular}
    \caption{\RMchange{Summary of performance results (in million particle updates per second) for each P4IRS and MD-Bench simulation runs on a single core of Ice Lake and Milan CPUs, and one A40 and A100 GPUs.}}
    \label{tab:md_particle_updates_per_second_cpu}
\end{table*}
